---
title: "NTP - Virtual Noise Audits"
output: 
  flexdashboard::flex_dashboard
    # :
    # storyboard: true
    # social: menu
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)    # For knitting document and include_graphics function
library(ggplot2)  # For plotting
library(png)      # For grabbing the dimensions of png files

# Images paths
img1_path <- "web/images/1_contestdescription.png"
img2_path <- "web/images/2_scenariodescription.png"
img3_path <- "web/images/3_mapofthearea.png"
img4_path <- "web/images/4_aerialview.png"
img5_path <- "web/images/5_3dview.png"
img6_path <- "web/images/6_viewpoint1.png"
img7_path <- "web/images/7_viewpoint2.png"
img8_path <- "web/images/8_shortmeasurements.png"
```

The contest
=========================================

Column
-----------------------------------------

### {data-commentary-width=0}

```{r}
include_graphics(img1_path)

```


Column
-----------------------------------------
### The contest 

#### Description

The Noise Training Project (NTP) wants to involve students and external experts in the improvement and testing of the new tool we are developing: Virtual Noise Audits. With this aim we want to make a **call for participants** within the attendees to the Workshop. Just participate performing an audit on our initial virtual scenario according to you country’s regulation. Make the audit, report your results and give us your feedback, please. 

- We ask for your collaboration in two different ways: a) perform a virtual audit, b) propose new scenarios. Apply to the awards just submitting your report or your proposal.
- As a gesture of appreciation, the winners of each category will receive an Amazon gift card worth 150 €. 
- The subscription to this contest will be available by email until **June 19th** (only to attendees to the workshop).
- The jury will be made up of members of the entities participating in the project. The personal data provided will only be used in issues related to the execution of the competition. Any other information provided might be used for scientific or academic goals of the project. All communications will be made by e-mail.



#### Best report award

- Make the virtual audit and report your results conforming your countries regulatory procedures
- You can spend a maximum of 2 pages to: a)  summarize the regulation and procedure you are applying (including country and region reference); b) report the audit results


#### Best new scenario award

- Propose scenarios that you consider relevant for the training of novel technicians or the assessment of their qualification and performance
- You can spend a maximum of 1 page to describe the sound sources involved, the challenges of this scenario, and to justify why it would be relevant for training or assessment of any students of an environmental acoustics training course.


Virtual scenario {.storyboard}
=========================================
### Virtual Noise Audit. General information.

```{r}
include_graphics(img2_path)
```


### Virtual Noise Audit. Map view of the scenario {data-commentary-width=400}

```{r}
include_graphics(img3_path)
```

*** 
Some text about the actibvity (probably the text present in the section of Activity details and noise details of the page before)

### Square – aerial view {data-commentary-width=400}

```{r}
include_graphics(img4_path)
```

*** 
This is the aerial view of the square. You can observe the limits of the activity, and the location of Viewpoint 1 and 2


### 3D view of the activity {data-commentary-width=400}

```{r}
include_graphics(img5_path)
```

*** 

This is a 3D view close to the limits of the activity. The activity is an outdoor bar with a small scenario in the front of it. Any music in this scenario is coming from this point.

### Pedestrian at location Viewpoint #1 {data-commentary-width=400}

```{r}
include_graphics(img6_path)
```

*** 
This is the view from location “Viewpoint #1”. Look at the map.

### Pedestrian at location Viewpoint #2 {data-commentary-width=400}

```{r}
include_graphics(img7_path)
```

*** 
This is the view from location “Viewpoint #2”. Look at the map.


### SHort measurements {data-commentary-width=400}

```{r}
include_graphics(img8_path)
```

*** 
You will have available measurements with an averaging time as small as 1 second (Leq1s). This is the time history (profile) of the measurements you can request (from 14:00 Sept 27th , to 	07:00 Sept 28th). You will also have recording obtained during that interval.