---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard
    # :
    # storyboard: true
    # social: menu
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)    # For knitting document and include_graphics function
library(ggplot2)  # For plotting
library(png)      # For grabbing the dimensions of png files

# Images paths
img1_path <- "web/images/1_contestdescription.png"
img2_path <- "web/images/2_scenariodescription.png"
img3_path <- "web/images/3_mapofthearea.png"
img4_path <- "web/images/4_aerialview.png"
img5_path <- "web/images/5_3dview.png"
img6_path <- "web/images/6_viewpoint1.png"
img7_path <- "web/images/7_viewpoint2.png"
img8_path <- "web/images/8_shortmeasurements.png"
```

Details
=========================================

Column
-----------------------------------------

### Descripción etiqueta 1 {data-commentary-width=0}

```{r}
include_graphics(img1_path)

```


### Virtual Noise Audit. General information.

```{r}
include_graphics(img2_path)
```


Analysis {.storyboard}
=========================================

### Virtual Noise Audit. Map view of the scenario {data-commentary-width=400}

```{r}
include_graphics(img3_path)
```

*** 
Some text about the actibvity (probably the text present in the section of Activity details and noise details of the page before)

### Square – aerial view {data-commentary-width=400}

```{r}
include_graphics(img4_path)
```

*** 
This is the aerial view of the square. You can observe the limits of the activity, and the location of Viewpoint 1 and 2


### 3D view of the activity {data-commentary-width=400}

```{r}
include_graphics(img5_path)
```

*** 

This is a 3D view close to the limits of the activity. The activity is an outdoor bar with a small scenario in the front of it. Any music in this scenario is coming from this point.

### Pedestrian at location Viewpoint #1 {data-commentary-width=400}

```{r}
include_graphics(img6_path)
```

*** 
This is the view from location “Viewpoint #1”. Look at the map.

### Pedestrian at location Viewpoint #2 {data-commentary-width=400}

```{r}
include_graphics(img7_path)
```

*** 
This is the view from location “Viewpoint #2”. Look at the map.


### SHort measurements {data-commentary-width=400}

```{r}
include_graphics(img8_path)
```

*** 
You will have available measurements with an averaging time as small as 1 second (Leq1s). This is the time history (profile) of the measurements you can request (from 14:00 Sept 27th , to 	07:00 Sept 28th). You will also have recording obtained during that interval.